### 2023-03-06 manuscript.tex
* manuscript.tex: Fix wrong regular expressions.
* manuscript.tex: Add chapter numbers in examples.
* manuscript.tex: Note on MSO transduction.

@@

Accordingly, the transduction is defined:

@@

\ex.
\a. \(a^{2n} \to a^{n}b^{n}\)
\b. \(a^{2n+1} \to a^{n+1}b^{n}\)

>>>>

\renewcommand{\ExLBr}{(\thechapter.}

@@

Accordingly, the transduction is defined:\footnote{Observant readers
  may notice that an efficient transducer implementing said
  transduction reads the input \textemph{twice}, dispatching on the
  number of \(a\)s in the first pass.  This is due to the
  correspondence between monadic second-order logic and two-way
  finite-state transducers.}

@@

\ex.
\a. \(a^{2n} \to (ab)^{n}\)
\b. \(a^{2n+1} \to (ab)^{n}a\)
